%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Akhil}{Singhal}{Contact: (+91) 8629015410 \\
Mail: \href{mailto:akhilsinghal1234@gmail.com}{akhilsinghal1234@gmail.com} \\
LinkedIn: \href{https://www.linkedin.com/in/akhil-singhal-a59448106/}{linkedin.com/in/akhil-singhal}

Github: \href{https://github.com/akhilsinghal1234}{github.com/akhilsinghal1234}
}


% \begin{center}
% \large \color{subheadings}\custombold{ }
% \end{center}
\vspace{8pt}
\section{Education}
\runsubsection{Indian Institute of Technology(IIT) Mandi}
\descript{| B.Tech in Computer Science}
\location{Expected June 2019 | Himachal Pradesh, India 
}
 \textbullet{} Cum. GPA: 8.8
\sectionsep

\runsubsection{SumerMal Jain Public School}
\descript{| Senior Sec. Education}
\location{ April 2015 | Delhi, India}
 \textbullet{} Percentage: 94.6\%
\sectionsep

\section{Experience}

\runsubsection{Siemens Technology and Services}
\descript{| Software Design and Testing Intern}
\location{Dec 2017 - Feb 2018 | Bengaluru, India}
\begin{tightemize}
\item Worked on Metric Driven Development(MDD) for
Intelligent Software Engineering.
\item Developed API to extract metrics for each source code in a Git repository in real-time(commit) and compare with previous versions.
\item Designed UI to visualize different use-cases important for tracking maintainability and development. 
\item Used ML techniques to predict bugs in Software iterations using Mozilla's-{\addfontfeatures{FakeBold=2.5}Bugzilla} Repository using source-code metrics.
\end{tightemize}
\sectionsep

\runsubsection{MothersonSumi Infotech \& Designs}
\descript{| Intern }
\location{June 2017 – Aug 2017 | Noida, India}
\begin{tightemize}
\item Completed project on Internet Of Things(IOT).
\item Used Arduino micro-controller to save different sensor values on online database and hosted a website for the same.
\item Designed UI to visualize the sensor values over time.
\end{tightemize}
\sectionsep


\section{Projects}

\runsubsection{3D-Gait Recognition} \\
\normalsize Using Deep learning techniques, developed a model to recognize human beings using 3D gait as a biometric. Used Machine Learning and Deep Learning models to generate mesh for human body for a given picture or video. Developed single pipeline to generate human body mesh, train and recognize human on the basis of the 3D gait.	\\

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{Pixlr}	\\
\normalsize Designed a dynamic Website - Pixlr, dedicated for the artists and
photographers to showcase their skills for Database project. Used MySQL as database, PHP \& JavaScript for back-end , HTML \& CSS for front-end development.\\
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{Automated Parking System(\textsc{APS})}	\\
\normalsize Developed a fully functional prototype for Android app controlled
Automated Parking System(APS) for college event - \textsc{Aavishkar}.\\
The prototype was designed as a solution to parking problems existing in urban areas.
\sectionsep

\begin{minipage}[t]{0.45\textwidth}
\section{Courses}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \large Database Systems.
\item Deep Learning and Data Mining.
\item Machine Learning and Artificial Intelligence.
\item System Practicum.
\item Advanced Data Structures and Algorithms.
\end{tightemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}



\section{Programming Languages}
\location{\large Over 5000 lines:}
\large \hspace{2mm} \textbullet{} C \textbullet{}  C++ \textbullet{} Python \\
\location{\large Over 1000 lines:}
\large \hspace{2mm} \textbullet{} CSS \textbullet{} PHP \textbullet{} MySQL\\
\location{\large  Familiar:}
\large \hspace{2mm} \textbullet{} Java  \textbullet{} Bash \textbullet{} Haskell \textbullet{} \LaTeX\\
\sectionsep
\end{minipage}

\newpage

\vspace*{8mm}
\section{Technical Skills}
\large{{\addfontfeatures{FakeBold=5.5}Back-end Development}}: Python, C++, Php.

\large{{\addfontfeatures{FakeBold=5.5}Front-end Development}}: HTML, CSS.

\large{{\addfontfeatures{FakeBold=5.5}Databases}}: MySQL, PostgreSQL, MongoDB, InfluxDB.

\large{{\addfontfeatures{FakeBold=5.5}Script}}: Python, Bash, Shell. 

\large{{\addfontfeatures{FakeBold=5.5}Others}}: Linux, Docker, VMs, Tensorlow, Keras. 
\sectionsep

\section{Achievements}
\begin{tightemize}
\vspace{\topsep}
\item First year branch topper with cum GPA : 9.36.
\item Secured 2\textsuperscript{nd} position in Aavishkar(intra IIT team event) for the APS.
\end{tightemize}

\section{Hobbies \& Interests}
\vspace{\topsep}
\begin{tightemize}
\item Data Structures and Algorithms
\item Big Data
\item Internet of Things(IoT)
\item Football, Hiking and trekking.
\end{tightemize}

\hfill
% \begin{minipage}[t]{.35\textwidth}
% \subsection{Spoken \& Written}
% \location{Native fluency:} English, Spanish\\
% \location{Reading fluency:} Chinese, Japanese\\
% \end{minipage}

\end{document}  \documentclass[]{article}
